\textbf{ \Large {Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-15 Paper/PaperJahrSchlich.tex
nn in shm implementation

\linenumbers % Schaltet Zeilennummerierung ein
\modulolinenumbers[5] % nur jede 5. Zeile
\section*{Dictionary}

\begin{tabular}{|l|l|}
\hline 
Sensorknoten (SunSPOT) & sensor node \\ 
\hline 
einzelner Messsensor (Thermometer) & sensor \\ 
\hline 
Knoten im neuronalen Netz & neuron \\ 
\hline 
eine abgeschlossene Messungreihe & test run \\ 
\hline 
gemessene Werte & sensor data \\ 
\hline 
vorhergesagte Werte & predicted data \\ 
\hline 
durch Vorhersage erwartete Werte & expected data \\ 
\hline 
einzelner Messwert & measurement \\ 
\hline 
Test & laboratory experiments\\ 
\hline
tatsächliche, nicht virtuelle Messung & actual measurement \\
\hline
Messaufbau & test setup \\
\hline

\end{tabular}

@@

\colorbox{cyan}{neuer Absatz:}
The SHM system is programmed object-oriented in Java. 
Object orientation uses objects, which are instanciated using classes as paradigm. 
A class includes methods, allowing the objects to perform actions, and attributes, storing object-specific data.
The SHM system consists of two packages---\texttt{sensornode} and \texttt{basestation}.
A package organizes several Java classes that build a program.

\autoref{fig:UML-sn} describes the classes of the \texttt{sensor\-node} package.
The package \texttt{sensor\-node} consists of the classes \texttt{Acceleration\-Sampler}, \texttt{FFT}, \texttt{Communi\-cation} and \texttt{Main\-Spot}, which are embedded directly into the sensor nodes.
The \texttt{Acceleration\-Sampler} class is responsible for measuring the acceleration.
There are two phases: \colorbox{cyan}{At} first, the acceleration is measured with a low sampling rate.
Once the acceleration exceeds a threshold, the \colorbox{cyan}{second phase is entered} by increasing the sampling rate. 
The measured values are stored into an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a FFT on the measured accelerations. 
With the transformed data, the magnitudes and the correlating frequencies of the measured oscillation are calculated.
Finally, the natural frequency \colorbox{cyan}{is} determined by extracting the maximal magnitude.
The \texttt{Communi\-cation} class opens a radio connection between the sensor node and the basestation to transfer data from the sensor node to the basestation.
For starting the operation of \colorbox{cyan}{the sensor node}, the entry point of the programm is the \texttt{start\-App()} method in the \texttt{Main\-Spot} class. 
Within the \texttt{Main\-Spot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class and the \texttt{Communication} class are created to perform the measurement.

>>>>

%----------------------------------------------------------------------------------------
%
%\linenumbers % Schaltet Zeilennummerierung ein
%\modulolinenumbers[5] % nur jede 5. Zeile
%\section*{Dictionary}
%
%\begin{tabular}{|l|l|}
%\hline 
%Sensorknoten (SunSPOT) & sensor node \\ 
%\hline 
%einzelner Messsensor (Thermometer) & sensor \\ 
%\hline 
%Knoten im neuronalen Netz & neuron \\ 
%\hline 
%eine abgeschlossene Messungreihe & test run \\ 
%\hline 
%gemessene Werte & sensor data \\ 
%\hline 
%vorhergesagte Werte & predicted data \\ 
%\hline 
%durch Vorhersage erwartete Werte & expected data \\ 
%\hline 
%einzelner Messwert & measurement \\ 
%\hline 
%Test & laboratory experiments\\ 
%\hline
%tatsächliche, nicht virtuelle Messung & actual measurement \\
%\hline
%Messaufbau & test setup \\
%\hline
%
%\end{tabular}

@@

\colorbox{cyan}{section ab hier teilweise neu (NN):}
The SHM system is programmed object-oriented in Java. 
Object orientation uses objects, which are instanciated using classes as paradigm. 
A class includes methods, allowing the objects to perform actions, and attributes, storing object-specific data.
The SHM system consists of two packages---\texttt{sensornode} and \texttt{basestation}.
A package organizes several Java classes that build a program.

\autoref{fig:UML-sn} describes the classes of the \texttt{sensor\-node} package.
The package \texttt{sensor\-node} consists of the classes \texttt{Acceleration\-Sampler}, \texttt{FFT}, \texttt{Measure\-ment}, \texttt{Network\-Training}, \texttt{Communi\-cation} and \texttt{Main\-Spot}, forming the SHM system, and several classes obtained from the Java library "SNIPE" \todo{Quelle für SNIPE!} that implement a framework for neural networks.
The classes are embedded directly into the sensor nodes.

The \texttt{Acceleration\-Sampler} class is responsible for measuring the acceleration.
There are two phases: \colorbox{cyan}{At} first, the acceleration is measured with a low sampling rate.
Once the acceleration exceeds a threshold, the \colorbox{cyan}{second phase is entered} by increasing the sampling rate. 
The measured values are stored into an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a FFT on the measured accelerations. 
With the transformed data, the magnitudes and the correlating frequencies of the measured oscillation are calculated.
Finally, the natural frequency \colorbox{cyan}{is} determined by extracting the maximal magnitude.

The \texttt{Measure\-ment} class defines analyzed measurements by storing the address of the sensor node, the maximal magnitude, the natural frequency and if a sensor defect was detected.
For every measurement, one object of the type \texttt{Measure\-ment} is instantiated.
Using the SNIPE library, a neural network is defined and created for fault detection.
The \texttt{Network\-Training} class defines a routine to train the neural network with prior measured \texttt{Measure\-ment} objects.
The \texttt{Communi\-cation} class opens a radio connection between the sensor node and the basestation to transfer the \texttt{Measure\-ment} objects from the sensor node to the basestation.
For starting the operation of \colorbox{cyan}{the sensor node}, the entry point of the programm is the \texttt{start\-App()} method in the \texttt{Main\-Spot} class. 
Within the \texttt{Main\-Spot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class, the SNIPE \texttt{Neural\-Network} class, the \texttt{Network\-Training} class and the \texttt{Communi\-cation} class are created to perform the measurement.
